CO Interlopers Eloping from [C~\textsc{ii}] Surveys

### 2019-03-23 paper/ms.tex
Fix fisher matrix
Add derivation of Fisher matrix

Ignoring interlopers and foreground contamination for a moment, we can
simplify this expression as
\beq\label{eq:fisher_nocontam}
\begin{split}
F_{i,j} =&
\int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} \denps^2(k) \\
\times & \left[ 
\sum_{l\neq i,j} \frac{B_l^2}{\pstot{l}\xps{i}{j} + \xps{i}{l}\xps{l}{j}}
+ \delta_{ij} \left( 
\sum_{l\neq i} \frac{B_l^2}{\xps{i}{l}^2 + \pstot{i}\pstot{l}}
+ \frac{1}{\pstot{i}\xps{\delta}{\delta} + \xps{i}{\delta}^2}
\right) \right. \\
& + (1-\delta_{ij}) \left(
\frac{B_i}{\pstot{i}\xps{j}{\delta} + \xps{i}{\delta}\xps{i}{j}}
+ \frac{B_j}{\pstot{j}\xps{i}{\delta} + \xps{j}{\delta}\xps{i}{j}}
+ \frac{B_iB_j}{\xps{i}{j}^2 + \pstot{i}\pstot{j}}
\right)
\Bigg]
\end{split}
\eeq

>>>>

Ignoring interlopers and foreground contamination for a moment, we can
simplify this expression as (see Appendix~\ref{app:fisher_deriv} for a
derivation):
\beq\label{eq:fisher_nocontam}
\begin{split}
F_{i,j} =&
\int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} \denps^2(k) \\
\times & \left[ 
\delta_{ij} \left( 
\sum_{l\neq i} \frac{B_l^2}{\xps{i}{l}^2 + \pstot{i}\pstot{l}}
+ \frac{1}{\pstot{i}\xps{\delta}{\delta} + \xps{i}{\delta}^2}
\right) \right. \\
&\left. + (1-\delta_{ij}) \left( 
\sum_{l\neq i,j} \frac{B_l^2}{\pstot{l}\xps{i}{j} + \xps{i}{l}\xps{l}{j}}
+\frac{B_i}{\pstot{i}\xps{j}{\delta} + \xps{i}{\delta}\xps{i}{j}}
+ \frac{B_j}{\pstot{j}\xps{i}{\delta} + \xps{j}{\delta}\xps{i}{j}}
+ \frac{B_iB_j}{\xps{i}{j}^2 + \pstot{i}\pstot{j}}
\right)
\right]\text{.}
\end{split}
\eeq
Including the auto-spectra in this analysis simply requires summing over all
$l$ values, replacing $\xps{i}{i}$ with $\pstot{i}$ \Gus{I think this is
correct?}.

\appendix

\section{Fisher Matrix Derivation}\label{app:fisher_deriv}
We show a derivation of Equation~\ref{eq:fisher_nocontam}. First, consider the
Fisher matrix from Equation~\ref{eq:co_fisher}.
\beq\label{eq:co_fisher_2}
F_{i,j} = 
\int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
\sum_{\substack{l,l'\\l > l'}} \sum_{\substack{m,m'\\m > m'}}
\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
\frac{1}{\Cov{\hat{P}_{l,l'}(k)}{\hat{P}_{m,m'}(k)}} 
\frac{\partial \hat{P}_{m,m'}(k)}{\partial B_j}\text{,}
\eeq
where $i$ and $j$ each refer to a line by its upper transitional level and the
$l$, $l'$, $m$ and $m'$ sum over all lines considered. We exploit the fact
that the Fisher matrix is unchanged under the substitution,
\begin{equation*}
\sum_{\substack{l,l'\\l > l'}} \rightarrow 
\frac{1}{2} \sum_{\substack{l,l'\\l \neq l'}}\text{.}
\end{equation*}
Next, we can write down the derivatives of the power spectra as,
\beq\label{eq:psderiv}
\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
= \left( B_{l'} \delta_{il} + B_l\delta_{il'} \right) \denps(k)\text{.}
\eeq
Now we can also write down the covariance formula as,
\beq\label{eq:cov}
\begin{aligned}
\left(\Cov{\hat{P}_{l,l'}}{\hat{P}_{m,m'}}\right)^{-1} = 
&(\pstot{l}\xps{l'}{m'} + \xps{l}{l'}\xps{l}{m'})^{-1} &&\times \delta_{lm} (1-\delta_{l'm'}) \\
&+ (\pstot{l}\xps{l'}{m} + \xps{l'}{l}\xps{l}{m})^{-1} &&\times \delta_{lm'} (1-\delta_{l'm}) \\
&+ (\pstot{l'}\xps{l}{m'} + \xps{l'}{l}\xps{l'}{m'})^{-1} &&\times \delta_{l'm} (1-\delta_{lm'}) \\
&+ (\pstot{l'}\xps{l}{m} + \xps{l'}{l}\xps{l'}{m})^{-1} &&\times \delta_{l'm'} (1-\delta_{lm}) \\
&+ (\xps{l}{l'}^2 + \pstot{l}\pstot{l'})^{-1} &&\times \delta_{lm} \delta_{l'm'} \\
&+ (\xps{l}{l'}^2 + \pstot{l}\pstot{l'})^{-1} &&\times \delta_{lm'} \delta_{l'm}\text{.}
\end{aligned}
\eeq
We are at liberty to distribute the inverse to all terms since upon inspection
of the Kronecker delta's one and only one term will contribute to the sum. In
the case that the covariance vanishes (e.g.
$\Cov{\hat{P}_{1,2}}{\hat{P}_{3,4}}=0$) we exclude this term from the sum in
Equation~\ref{eq:co_fisher_2}. Since the product,
\begin{equation*}
\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
% \frac{1}{\Cov{\hat{P}_{l,l'}(k)}{\hat{P}_{m,m'}(k)}} 
\frac{\partial \hat{P}_{m,m'}(k)}{\partial B_j}
\end{equation*}
is symmetric under $(l,l',m,m') \rightarrow (l',l,m',m)$\footnote{and the
summation is as well}, we can equivalently use the following formula for the
covariance:
\beq\label{eq:cov_simple}
\begin{aligned}
\left(\Cov{\hat{P}_{l,l'}}{\hat{P}_{m,m'}}\right)^{-1} = 
&4 (\pstot{l}\xps{l'}{m'} + \xps{l}{l'}\xps{l}{m'})^{-1} &&\times \delta_{lm} (1-\delta_{l'm'}) \\
&+ 2(\xps{l}{l'}^2 + \pstot{l}\pstot{l'})^{-1} &&\times \delta_{lm} \delta_{l'm'}\text{.}
\end{aligned}
\eeq
Combining these facts we can arrive at the following formula for the Fisher matrix:
\beq\label{eq:co_fisher_explicity}
\begin{split}
F_{i,j} = 
\frac{1}{4} \int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
\denps(k)^2
\sum_{\substack{l,l'\\l \neq l'}} \sum_{\substack{m,m'\\m \neq m'}}
&\left( B_{l'} \delta_{il} + B_l\delta_{il'} \right)
\left( B_{m'} \delta_{jm} + B_m\delta_{jm'} \right) \\
\times&\left( \frac{4}{\pstot{l}\xps{l'}{m'} + \xps{l}{l'}\xps{l}{m'}} \delta_{lm} (1-\delta_{l'm'})
+ \frac{2}{\xps{l}{l'}^2 + \pstot{l}\pstot{l'}} \delta_{lm} \delta_{l'm'}\right)
\text{.}
\end{split}
\eeq
This formula can be expanded and simplified to give Equation~\ref{eq:fisher_nocontam}.
